Query Optimization for Dynamic Imputation

### 2017-03-01 paper/algorithm.tex
paper: clarified definition of Loss in text, as per sam's feedback

\srm{I find this table hard to follow -- I think it'd be good to explain one or two of the rows in detail, and to explain what the set L contains.}
Using the drop operator incurs a loss of information of 1 (i.e. we lose all information that
the dropped tuples might have encoded). 
\todobox{fix this explanation, not inverseley proprtional to what is stated here}{Imputing \nullv{} fields incurs a loss penalty $p \in (0, 1]$,
which is inversely proportional to the number of total cells available to train the imputation algorithm. 
Total cells are defined as the product of the number of attributes and the number of tuples.
Intuitively, imputation
accuracy \textit{increases} when more complete attributes and complete tuples are available;
correspondingly, the information lost \textit{decreases} with more values to work
with.}
Since we conceive that
alternate imputation strategies could be used, the analyst may provide a corresponding
loss with a reasonable parameterization.

>>>>

Each imputation operator incurs a heuristic loss penalty. We define \textsc{Loss} as the average over the individual penalties incurred
by $\mu,\delta$ operators. Our recursive definition of $L$ accumulates these penalties in a multi-set, as the order of the penalties is irrelevant,
and averages them at the root of the plan. For example, $\delta$ contributes a loss of 1 (i.e. we lose all information  that dropped tuples
might have encoded). Meanwhile, imputing \nullv{} fields with $\mu$ incurs a loss penalty $p \in (0, 1]$. In this case, the penalty is
inversely proportional to the square root of the number of cells available to train the imputation algorithm, which is defined as
as the product of the number of attributes and the number of tuples. Intuitively, imputation
accuracy \textit{increases} when more complete attributes and complete tuples are available;
correspondingly, the information lost \textit{decreases} with more values to work
with. The square root captures the intuition that the benefits provided by more training observations has diminishing returns.

Since we conceive that
alternate imputation strategies could be used, the analyst may provide a corresponding
loss with a reasonable parameterization.
